---
title: "Data Science Challenge Solution"
author: "QiHan Zhao"
date: "1/14/2022"
output: pdf_document
---
```{r import-libraries, echo=FALSE, results="hide"}
library(tidyverse)
library(ggplot2)
library(readr)
```

# Question 1

On Shopify, we have exactly 100 sneaker shops, and each of these shops sells only one model of shoe. We want to do some analysis of the average order value (AOV). When we look at orders data over a 30 day window, we naively calculate an AOV of $3145.13. Given that we know these shops are selling sneakers, a relatively affordable item, something seems wrong with our analysis. 

```{r import dataset, include=FALSE}
shopData <- read_csv("~/Desktop/DataAnalytics/shopifyInternChallenge/2019 Winter Data Science Intern Challenge Data Set - Sheet1.csv")
```

## A. Think about what could be going wrong with our calculation. Think about a better way to evaluate this data.

First, I want to check if there is any missing value in the columns 'order_amount'
and 'total_items', since the two directly tie to the calculation of AOV:

```{r check-NA}
shopData%>%
  select(order_amount, total_items)%>%
  summarize(NA.in.Order.Amount = sum(is.na(order_amount)), 
            NA.in.Total.items = sum(is.na(total_items)))
```
Since there are no missing values, I would proceed to check for the range of values the variable 'order_amount' take:
```{r range-OrderAmount}
summary(shopData$order_amount)
```
I also checked the range of values for 'total_items': 
```{r range-OrderNumbers}
summary(shopData$total_items)
```

Based on the two outputs, I would propose that one possible cause to the 
unrealistically high AOV is that the value is calculated through averaging total 
earnings over the numbers of entries in the dataset, instead of the actual number
of orders. Because there are some extreme values in the trade deals, calculating 
AOV in the former way would pull the value to a much higher number than it should
be.

### Alternative 1:
The simplest alternative is to average the total amount over the total number of
orders in the 30-days window:
```{r overall-mean}
sum(shopData$order_amount)/sum(shopData$total_items)
```
This value is much more realistic than the given $3145.13, but it treats all 100
shops as one entity and fails to take into account how "well" each store is doing. 
Therefore, the following alternatives are all based on averaging each store's own
AOV, which I believe reflects the market better for the shop owners.

```{r avearage-store-aov}
aov <- shopData%>%
  group_by(shop_id)%>%
  summarize(totalOrders = sum(total_items), 
            aov = sum(order_amount)/totalOrders)
```


### Alternative 2:
In this alternative, I will calculate the metric using the average of the shops' 
individual AOV. But first, I will check to see if any shop is selling very 
expensive sneakers. These shops are likely to be the minority in the market, but
their AOV may pull the metric up depending on how high the former is:
```{r aov-check-extremeVal}
aov%>%
  arrange(desc(aov))
```
As we can see from the output, shop 78's AOV is $25725, which is much higher than 
the rest of the shops. Since it is just one of the shops, I will calculate the 
average after dropping it from the dataset. 
```{r aov-mean}
aov%>%
  filter(aov < 1000)%>%
  summarize(Average.AOV.of.All = trunc(mean(aov)))
```

### Alternative 3:
In the first alternative metric, I calculated the mean. However, I didn't check
the distribution of the data and I suspected that real-world data like this is 
likely to not follow a nice normal distribution, which makes mean a less desirable
metric. 
```{r aov-histogram}
ggplot(data=aov,aes(x=aov))+
  geom_histogram(binwidth=15)+
  coord_cartesian(xlim=c(0,1000))+
  theme_bw()
```
I'd argue that the histogram of shop AOV, excluding shop 78, is a bit left-skewed
and there is clearly an outlier that is just below 375. Therefore, I would use 
the median instead of the mean as the former is more robust, especially to outlier(s);
though it can be argued histogram graph may be variant depending on the bin width
that is used, the histogram above complied with the distribution I had for the data in my
mind after looking at the dataset in the previous question. 
```{r aov-med}
aov%>%
  summarize(med = median(aov))
```



